Supporting Information for\\ ``A weakly structured stem for human origins in Africa''

### 2023-01-07 supplement.tex
final fits and LLs

\begin{table}[ht]
\caption{
    \label{tab:supp-single-origin}
    \textbf{Best-fit parameters from the single-origin model.}
    This model includes a single stem population that splits into contemporary human
    groups. Fixed parameters are specified in Table~\ref{tab:fixed-params}.
    Inferred values are scaled to physical units assuming a generation time of
    29 years. This model gave a log-likelihood of -189,434.
}
\centering
\begin{tabular}[t]{rP{8cm}cc}
    \toprule
    Parameter & Description & Value & 95\% CI \\
    \midrule
    $N_e$ & Ancestral effective population size & 9860 & 9600--10090 \\
    $N_{MH}$ & Size of human lineage between Neanderthal and Nama splits & 20850 & 20640--21220 \\
    $N_{Nama_0}$ & Initial Nama size & 10170 & 9950--10250 \\
    $N_{Nama_F}$ & Final Nama size & 222 & 217--226 \\
    $N_{MSL_0}$ & Initial Mende size & 17280 & 16770--17490 \\
    $N_{MSL_F}$ & Final Mende size & 16730 & 16370--17060 \\
    $N_{EA}$ & Size of East African branch & 7130 & 6940--7130 \\
    $N_{Gumuz_F}$ & Final Gumuz size & 3800 & 3690--3900 \\
    $N_{EP}$ & East African agriculturist size & 12990 & 12720--13140 \\
    $N_{GBR_0}$ & Initial British size & 845 & 836--862 \\
    $N_{GBR_F}$ & Final British size & 12140 & 11870--12300 \\
    $N_{Neand}$ & Neanderthal size & 1850 & 1650--1990 \\
    $T_{Nama}$ & Nama split time (years) & 110900 & 107800--112200 \\
    $m_{Nama-MSL}$ & Nama--Mende symmetric migration rate & $2.83\times10^{-5}$ & $2.61\times10^{-5}$--$3.02\times10^{-5}$ \\
    $m_{Nama-EA}$ & Nama--East Africa symmetric migration rate & $4.98\times10^{-5}$ & $4.82\times10^{-5}$--$5.31\times10^{-5}$ \\
    $m_{MSL-EA}$ & Mende--East Africa migration rate & $18.7\times10^{-5}$ & $18.7\times10^{-5}$--$19.2\times10^{-5}$ \\
    $m_{EA-GBR}$ & East Africa--Europe migration rate & $4.38\times10^{-5}$ & $4.13\times10^{-5}$--$4.54\times10^{-5}$ \\
    $m_{EA-EA}$ & Intra-East Africa migration rate & $43.8\times10^{-5}$ & $41.0\times10^{-5}$--$44.2\times10^{-5}$ \\
    $f_{GBR \rightarrow EP}$ & Ancestry proportion of East African agriculturalists from GBR 12ka ($1-f$ from Gumuz) & 0.661 & 0.657--0.671 \\
    $f_{EP \rightarrow Nama}$ & Ancestry proportion from EA pastoralists to Nama 2ka & 0.280 & 0.270--0.286 \\
    $f_{GBR \rightarrow Nama}$ & Ancestry proportion from Europeans to Nama 10 generations ago & 0.150 & 0.147--0.154 \\
    \bottomrule
\end{tabular}
\end{table}

\begin{table}[ht]
\caption{
    \label{tab:supp-continuous-migration-no-mig}
    \textbf{Best-fit parameters from the Continuous-Migration model without stem migration.}
    Inferred values are scaled to physical units assuming a generation time of
    29 years. This model gave a log-likelihood of -126,644. This model allows for
    continuous migration between Stem 2 and contemporary populations, but disallows
    migration between Stem 2 and Stem 1, which later splits into branches leading
    to South, East, and West African populations.
}
\centering
\begin{tabular}[t]{rP{8cm}cc}
    \toprule
    Parameter & Description & Value & 95\% CIs \\
    \midrule
    $N_e$ & Ancestral effective population size & 10980 & 10810--11260 \\
    $N_{stem1}$ & Size of stem 1 lineage between Neanderthal and Nama splits & 13980 & 13930--15330 \\
    $N_{stem2}$ & Size of stem 2 lineage & 10390 & 9780--11250 \\
    $N_{Nama_0}$ & Initial Nama size & 11240 & 10760--11280 \\
    $N_{Nama_F}$ & Final Nama size & 221 & 216--226 \\
    $N_{MSL_0}$ & Initial Mende size & 10810 & 10510--11090 \\
    $N_{MSL_F}$ & Final Mende size & 25080 & 24050--25780 \\
    $N_{EA}$ & Size of East African branch & 7130 & 6970--7200 \\
    $N_{Gumuz_F}$ & Final Gumuz size & 3770 & 2650--3860 \\
    $N_{EP}$ & East African agriculturist size & 13070 & 12830--13250 \\
    $N_{GBR_0}$ & Initial British size & 946 & 931--964 \\
    $N_{GBR_F}$ & Final British size & 11560 & 11320--11760 \\
    $N_{Neand}$ & Neanderthal size & 2290 & 2140--2450 \\
    $T_{stems}$ & Stem split time (years) & 459700 & 446600--463300 \\
    $T_{Nama}$ & Nama split time (years) & 145400 & 137300--146000 \\
    $m_{Nama-MSL}$ & Nama--Mende symmetric migration rate & $1.46\times10^{-5}$ & $1.36\times10^{-5}$--$1.81\times10^{-5}$ \\
    $m_{Nama-EA}$ & Nama--East Africa symmetric migration rate & $4.22\times10^{-5}$ & $4.08\times10^{-5}$--$4.60\times10^{-5}$ \\
    $m_{MSL-EA}$ & Mende--East Africa migration rate & $20.8\times10^{-5}$ & $20.7\times10^{-5}$--$21.3\times10^{-5}$ \\
    $m_{EA-GBR}$ & East Africa--Europe migration rate & $4.36\times10^{-5}$ & $4.19\times10^{-5}$--$4.58\times10^{-5}$ \\
    $m_{EA-EA}$ & Intra-East Africa migration rate & $35.8\times10^{-5}$ & $34.6\times10^{-5}$--$37.0\times10^{-5}$ \\
    $f_{GBR \rightarrow EP}$ & Ancestry proportion of East African agriculturalists from GBR 12ka ($1-f$ from Gumuz) & 0.651 & 0.644--0.660 \\
    $f_{EP \rightarrow Nama}$ & Ancestry proportion from EA pastoralists to Nama 2ka & 0.271 & 0.264--0.279 \\
    $f_{GBR \rightarrow Nama}$ & Ancestry proportion from Europeans to Nama 10 generations ago & 0.153 & 0.148--0.156 \\
    $m_{stems}$ & Stem 1--stem 2 migration rate & $0$ & fixed \\
    $m_{stem2-Nama}$ & Stem 2--Nama migration rate & $5.63\times10^{-5}$ & $4.91\times10^{-5}$--$5.92\times10^{-5}$ \\
    $m_{stem2-MSL}$ & Stem 2--Mende migration rate & $14.2\times10^{-5}$ & $12.4\times10^{-5}$--$14.4\times10^{-5}$ \\
    $m_{stem2-EA}$ & Stem 2--East Africa migration rate & $3.82\times10^{-5}$ & $3.04\times10^{-5}$--$3.95\times10^{-5}$ \\
    \bottomrule
\end{tabular}
\end{table}

\begin{table}[ht]
\caption{
    \label{tab:supp-continuous-migration}
    \textbf{Best-fit parameters from the Continuous-Migration model.}
    Inferred values are scaled to physical units assuming a generation time of
    29 years. This model gave a log-likelihood of -115,500.
}
\centering
\begin{tabular}[t]{rP{8cm}cc}
    \toprule
    Parameter & Description & Value & 95\% CIs\\
    \midrule
    $N_e$ & Ancestral effective population size & 7270 & 4180--6530 \\
    $N_{stem1}$ & Size of stem 1 lineage between Neanderthal and Nama splits & 8260 & 7130--8400 \\
    $N_{stem2}$ & Size of stem 2 lineage & 13550 & 11330--13580 \\
    $N_{Nama_0}$ & Initial Nama size & 11940 & 11160--12390 \\
    $N_{Nama_F}$ & Final Nama size & 221 & 215--226 \\
    $N_{MSL_0}$ & Initial Mende size & 9740 & 9500--10210 \\
    $N_{MSL_F}$ & Final Mende size & 28150 & 25930--28930 \\
    $N_{EA}$ & Size of East African branch & 7490 & 7270--7630 \\
    $N_{Gumuz_F}$ & Final Gumuz size & 3730 & 3560--3810 \\
    $N_{EP}$ & East African agriculturist size & 13070 & 12800--13290 \\
    $N_{GBR_0}$ & Initial British size & 959 & 940--981 \\
    $N_{GBR_F}$ & Final British size & 11820 & 11490--12090 \\
    $N_{Neand}$ & Neanderthal size & 2670 & 2380--27950 \\
    $T_{stems}$ & Stem split time (years) & 1163000 & 1120000--1382000 \\ %%% Outside CI!!!
    $T_{Nama}$ & Nama split time (years) & 134700 & 127800--139900 \\
    $m_{Nama-MSL}$ & Nama--Mende symmetric migration rate & $0.98\times10^{-5}$ & $0.41\times10^{-5}$--$1.43\times10^{-5}$ \\
    $m_{Nama-EA}$ & Nama--East Africa symmetric migration rate & $4.08\times10^{-5}$ & $3.92\times10^{-5}$--$4.56\times10^{-5}$ \\
    $m_{MSL-EA}$ & Mende--East Africa migration rate & $21.4\times10^{-5}$ & $21.2\times10^{-5}$--$21.8\times10^{-5}$ \\
    $m_{EA-GBR}$ & East Africa--Europe migration rate & $4.17\times10^{-5}$ & $3.77\times10^{-5}$--$4.33\times10^{-5}$ \\
    $m_{EA-EA}$ & Intra-East Africa migration rate & $33.6\times10^{-5}$ & $33.0\times10^{-5}$--$36.3\times10^{-5}$ \\
    $f_{GBR \rightarrow EP}$ & Ancestry proportion of East African agriculturalists from GBR 12ka ($1-f$ from Gumuz) & 0.642 & 0.639--0.656 \\
    $f_{EP \rightarrow Nama}$ & Ancestry proportion from EA pastoralists to Nama 2ka & 0.255 & 0.245--0.263 \\
    $f_{GBR \rightarrow Nama}$ & Ancestry proportion from Europeans to Nama 10 generations ago & 0.156 & 0.151--0.160 \\
    $m_{stems}$ & Stem 1--stem 2 migration rate & $6.43\times10^{-5}$ & $6.14\times10^{-5}$--$7.83\times10^{-5}$ \\
    $m_{stem2-Nama}$ & Stem 2--Nama migration rate & $5.82\times10^{-5}$ & $4.50\times10^{-5}$--$7.04\times10^{-5}$ \\
    $m_{stem2-MSL}$ & Stem 2--Mende migration rate & $16.4\times10^{-5}$ & $13.8\times10^{-5}$--$18.9\times10^{-5}$ \\
    $m_{stem2-EA}$ & Stem 2--East Africa migration rate & $3.10\times10^{-5}$ & $2.18\times10^{-5}$--$3.65\times10^{-5}$ \\
    \bottomrule
\end{tabular}
\end{table}

\begin{table}[ht]
\caption{
    \label{tab:supp-merger-without-stem-migration}
    \textbf{Best-fit parameters from the Merger-Without-Stem-Migration model.}
    Inferred values are scaled to physical units assuming a generation time of
    29 years. This model gave a log-likelihood of -107,652.
}
\centering
\begin{tabular}[t]{rP{8cm}cc}
    \toprule
    Parameter & Description & Value & 95\% CIs\\
    \midrule
    $N_e$ & Ancestral effective population size & 11410 & 10100--11290 \\
    $N_{stem1}$ & Size of stem 1 lineage between stem 1--stem 2 split and stem 1E--stem 1S split & 102 & 113--606 \\
    $N_{stem2}$ & Size of stem 2 lineage & 24720 & 26500--35060 \\
    $N_{Nama_0}$ & Initial Nama and stem 1S size & 13180 & 11310--12910 \\
    $N_{Nama_F}$ & Final Nama size & 224 & 223--238 \\
    $N_{MSL_0}$ & Initial Mende size & 11760 & 10280--11630 \\
    $N_{MSL_F}$ & Final Mende size & 25770 & 25720--30180 \\
    $N_{EA}$ & Size of East African and stem 1E branch & 9190 & 8680--9140 \\
    $N_{Gumuz_F}$ & Final Gumuz size & 3360 & 3270--3470 \\
    $N_{EP}$ & East African agriculturist size & 13590 & 13120--13690 \\
    $N_{GBR_0}$ & Initial British size & 936 & 920--963 \\
    $N_{GBR_F}$ & Final British size & 12080 & 11790--12430 \\
    $N_{Neand}$ & Neanderthal size & 1950 & 1770--2110 \\
    $T_{stems}$ & Stem split time (years) & 415100 & 381400--410700 \\
    $T_{stem1}$ & Stem 1 split time into stem 1E and stem 1S (years) & 360700 & 154300--320400 \\
    $m_{Nama-MSL}$ & Nama--Mende symmetric migration rate & $0.523\times10^{-5}$ & $0.205\times10^{-5}$--$0.697\times10^{-5}$ \\
    $m_{Nama-EA}$ & Nama--East Africa symmetric migration rate & $4.09\times10^{-5}$ & $3.90\times10^{-5}$--$4.42\times10^{-5}$ \\
    $m_{MSL-EA}$ & Mende--East Africa migration rate & $19.5\times10^{-5}$ & $19.8\times10^{-5}$--$20.8\times10^{-5}$ \\
    $m_{EA-GBR}$ & East Africa--Europe migration rate & $3.74\times10^{-5}$ & $3.34\times10^{-5}$--$3.95\times10^{-5}$ \\
    $m_{EA-EA}$ & Intra-East Africa migration rate & $30.7\times10^{-5}$ & $35.2\times10^{-5}$--$39.6\times10^{-5}$ \\
    $f_{GBR \rightarrow EP}$ & Ancestry proportion of East African agriculturalists from GBR 12ka ($1-f$ from Gumuz) & 0.648 & 0.641--0.661 \\
    $f_{EP \rightarrow Nama}$ & Ancestry proportion from EA pastoralists to Nama 2ka & 0.259 & 0.245--0.264 \\
    $f_{GBR \rightarrow Nama}$ & Ancestry proportion from Europeans to Nama 10 generations ago & 0.156 & 0.152--0.161 \\
    $m_{stems}$ & Stem 1--stem 2 migration rate & $0$ & fixed \\
    $T_{Nama}$ & Time of Nama merger event & 118200 & 101400--116800 \\
    $f_{stem 2 \rightarrow Nama}$ & Proportion of stem 2 ancestry making up initial Nama lineage ($1-f$ from stem 1S) & 0.693 & 0.706--0.769 \\
    $T_{EA}$ & Time of East Africa merger event & 94300 & 94500--101400 \\
    $f_{stem 2 \rightarrow EA}$ & Proportion of stem 2 ancestry making up initial East Africa lineage ($1-f$ from stem 1E) & 0.497 & 0.510--0.564 \\
    $T_{MSL}$ & Time of secondary admixture from stem 2 to Mende & 23890 & 22920--25510 \\
    $f_{stem 2 \rightarrow MSL}$ & Proportion of ancestry from secondary stem 2 admixture to Mende & 0.171 & 0.174--0.196 \\
    \bottomrule
\end{tabular}
\end{table}

>>>>

\begin{table}[ht]
\caption{
    \label{tab:supp-single-origin}
    \textbf{Best-fit parameters from the single-origin model.}
    This model includes a single stem population that splits into contemporary human
    groups. Fixed parameters are specified in Table~\ref{tab:fixed-params}.
    Inferred values are scaled to physical units assuming a generation time of
    29 years. This model gave a log-likelihood of -189,271.
}
\centering
\begin{tabular}[t]{rP{8cm}cc}
    \toprule
    Parameter & Description & Value & 95\% CI \\
    \midrule
    $N_e$ & Ancestral effective population size & 9860 & 9600--10090 \\
    $N_{MH}$ & Size of human lineage between Neanderthal and Nama splits & 20850 & 20640--21220 \\
    $N_{Nama_0}$ & Initial Nama size & 10170 & 9950--10250 \\
    $N_{Nama_F}$ & Final Nama size & 222 & 217--226 \\
    $N_{MSL_0}$ & Initial Mende size & 17280 & 16770--17490 \\
    $N_{MSL_F}$ & Final Mende size & 16730 & 16370--17060 \\
    $N_{EA}$ & Size of East African branch & 7130 & 6940--7130 \\
    $N_{Gumuz_F}$ & Final Gumuz size & 3800 & 3690--3900 \\
    $N_{EP}$ & East African agriculturist size & 12990 & 12720--13140 \\
    $N_{GBR_0}$ & Initial British size & 845 & 836--862 \\
    $N_{GBR_F}$ & Final British size & 12140 & 11870--12300 \\
    $N_{Neand}$ & Neanderthal size & 1850 & 1650--1990 \\
    $T_{Nama}$ & Nama split time (years) & 110900 & 107800--112200 \\
    $m_{Nama-MSL}$ & Nama--Mende symmetric migration rate & $2.83\times10^{-5}$ & $2.61\times10^{-5}$--$3.02\times10^{-5}$ \\
    $m_{Nama-EA}$ & Nama--East Africa symmetric migration rate & $4.98\times10^{-5}$ & $4.82\times10^{-5}$--$5.31\times10^{-5}$ \\
    $m_{MSL-EA}$ & Mende--East Africa migration rate & $18.7\times10^{-5}$ & $18.7\times10^{-5}$--$19.2\times10^{-5}$ \\
    $m_{EA-GBR}$ & East Africa--Europe migration rate & $4.38\times10^{-5}$ & $4.13\times10^{-5}$--$4.54\times10^{-5}$ \\
    $m_{EA-EA}$ & Intra-East Africa migration rate & $43.8\times10^{-5}$ & $41.0\times10^{-5}$--$44.2\times10^{-5}$ \\
    $f_{GBR \rightarrow EP}$ & Ancestry proportion of East African agriculturalists from GBR 12ka ($1-f$ from Gumuz) & 0.661 & 0.657--0.671 \\
    $f_{EP \rightarrow Nama}$ & Ancestry proportion from EA pastoralists to Nama 2ka & 0.280 & 0.270--0.286 \\
    $f_{GBR \rightarrow Nama}$ & Ancestry proportion from Europeans to Nama 10 generations ago & 0.150 & 0.147--0.154 \\
    \bottomrule
\end{tabular}
\end{table}

\begin{table}[ht]
\caption{
    \label{tab:supp-continuous-migration-no-mig}
    \textbf{Best-fit parameters from the Continuous-Migration model without stem migration.}
    Inferred values are scaled to physical units assuming a generation time of
    29 years. This model gave a log-likelihood of -126,540. This model allows for
    continuous migration between Stem 2 and contemporary populations, but disallows
    migration between Stem 2 and Stem 1, which later splits into branches leading
    to South, East, and West African populations.
}
\centering
\begin{tabular}[t]{rP{8cm}cc}
    \toprule
    Parameter & Description & Value & 95\% CIs \\
    \midrule
    $N_e$ & Ancestral effective population size & 10980 & 10810--11260 \\
    $N_{stem1}$ & Size of stem 1 lineage between Neanderthal and Nama splits & 13980 & 13930--15330 \\
    $N_{stem2}$ & Size of stem 2 lineage & 10390 & 9780--11250 \\
    $N_{Nama_0}$ & Initial Nama size & 11240 & 10760--11280 \\
    $N_{Nama_F}$ & Final Nama size & 221 & 216--226 \\
    $N_{MSL_0}$ & Initial Mende size & 10810 & 10510--11090 \\
    $N_{MSL_F}$ & Final Mende size & 25080 & 24050--25780 \\
    $N_{EA}$ & Size of East African branch & 7130 & 6970--7200 \\
    $N_{Gumuz_F}$ & Final Gumuz size & 3770 & 2650--3860 \\
    $N_{EP}$ & East African agriculturist size & 13070 & 12830--13250 \\
    $N_{GBR_0}$ & Initial British size & 946 & 931--964 \\
    $N_{GBR_F}$ & Final British size & 11560 & 11320--11760 \\
    $N_{Neand}$ & Neanderthal size & 2290 & 2140--2450 \\
    $T_{stems}$ & Stem split time (years) & 459700 & 446600--463300 \\
    $T_{Nama}$ & Nama split time (years) & 145400 & 137300--146000 \\
    $m_{Nama-MSL}$ & Nama--Mende symmetric migration rate & $1.46\times10^{-5}$ & $1.36\times10^{-5}$--$1.81\times10^{-5}$ \\
    $m_{Nama-EA}$ & Nama--East Africa symmetric migration rate & $4.22\times10^{-5}$ & $4.08\times10^{-5}$--$4.60\times10^{-5}$ \\
    $m_{MSL-EA}$ & Mende--East Africa migration rate & $20.8\times10^{-5}$ & $20.7\times10^{-5}$--$21.3\times10^{-5}$ \\
    $m_{EA-GBR}$ & East Africa--Europe migration rate & $4.36\times10^{-5}$ & $4.19\times10^{-5}$--$4.58\times10^{-5}$ \\
    $m_{EA-EA}$ & Intra-East Africa migration rate & $35.8\times10^{-5}$ & $34.6\times10^{-5}$--$37.0\times10^{-5}$ \\
    $f_{GBR \rightarrow EP}$ & Ancestry proportion of East African agriculturalists from GBR 12ka ($1-f$ from Gumuz) & 0.651 & 0.644--0.660 \\
    $f_{EP \rightarrow Nama}$ & Ancestry proportion from EA pastoralists to Nama 2ka & 0.271 & 0.264--0.279 \\
    $f_{GBR \rightarrow Nama}$ & Ancestry proportion from Europeans to Nama 10 generations ago & 0.153 & 0.148--0.156 \\
    $m_{stems}$ & Stem 1--stem 2 migration rate & $0$ & fixed \\
    $m_{stem2-Nama}$ & Stem 2--Nama migration rate & $5.63\times10^{-5}$ & $4.91\times10^{-5}$--$5.92\times10^{-5}$ \\
    $m_{stem2-MSL}$ & Stem 2--Mende migration rate & $14.2\times10^{-5}$ & $12.4\times10^{-5}$--$14.4\times10^{-5}$ \\
    $m_{stem2-EA}$ & Stem 2--East Africa migration rate & $3.82\times10^{-5}$ & $3.04\times10^{-5}$--$3.95\times10^{-5}$ \\
    \bottomrule
\end{tabular}
\end{table}

\begin{table}[ht]
\caption{
    \label{tab:supp-continuous-migration}
    \textbf{Best-fit parameters from the Continuous-Migration model.}
    Inferred values are scaled to physical units assuming a generation time of
    29 years. This model gave a log-likelihood of -115,280.
}
\centering
\begin{tabular}[t]{rP{8cm}cc}
    \toprule
    Parameter & Description & Value & 95\% CIs\\
    \midrule
    $N_e$ & Ancestral effective population size & 6090 & 4180--6530 \\
    $N_{stem1}$ & Size of stem 1 lineage between Neanderthal and Nama splits & 8080 & 7130--8400 \\
    $N_{stem2}$ & Size of stem 2 lineage & 12340 & 11330--13580 \\
    $N_{Nama_0}$ & Initial Nama size & 11860 & 11160--12390 \\
    $N_{Nama_F}$ & Final Nama size & 221 & 215--226 \\
    $N_{MSL_0}$ & Initial Mende size & 9880 & 9500--10210 \\
    $N_{MSL_F}$ & Final Mende size & 27730 & 25930--28930 \\
    $N_{EA}$ & Size of East African branch & 7460 & 7270--7630 \\
    $N_{Gumuz_F}$ & Final Gumuz size & 3730 & 3560--3810 \\
    $N_{EP}$ & East African agriculturist size & 13110 & 12800--13290 \\
    $N_{GBR_0}$ & Initial British size & 951 & 940--981 \\
    $N_{GBR_F}$ & Final British size & 11874 & 11490--12090 \\
    $N_{Neand}$ & Neanderthal size & 2620 & 2380--27950 \\
    $T_{stems}$ & Stem split time (years) & 1223000 & 1199000--1382000 \\
    $T_{Nama}$ & Nama split time (years) & 134200 & 127800--139900 \\
    $m_{Nama-MSL}$ & Nama--Mende symmetric migration rate & $0.92\times10^{-5}$ & $0.41\times10^{-5}$--$1.43\times10^{-5}$ \\
    $m_{Nama-EA}$ & Nama--East Africa symmetric migration rate & $4.11\times10^{-5}$ & $3.92\times10^{-5}$--$4.56\times10^{-5}$ \\
    $m_{MSL-EA}$ & Mende--East Africa migration rate & $21.3\times10^{-5}$ & $21.2\times10^{-5}$--$21.8\times10^{-5}$ \\
    $m_{EA-GBR}$ & East Africa--Europe migration rate & $4.16\times10^{-5}$ & $3.77\times10^{-5}$--$4.33\times10^{-5}$ \\
    $m_{EA-EA}$ & Intra-East Africa migration rate & $33.7\times10^{-5}$ & $33.0\times10^{-5}$--$36.3\times10^{-5}$ \\
    $f_{GBR \rightarrow EP}$ & Ancestry proportion of East African agriculturalists from GBR 12ka ($1-f$ from Gumuz) & 0.642 & 0.639--0.656 \\
    $f_{EP \rightarrow Nama}$ & Ancestry proportion from EA pastoralists to Nama 2ka & 0.255 & 0.245--0.263 \\
    $f_{GBR \rightarrow Nama}$ & Ancestry proportion from Europeans to Nama 10 generations ago & 0.155 & 0.151--0.160 \\
    $m_{stems}$ & Stem 1--stem 2 migration rate & $6.26\times10^{-5}$ & $6.14\times10^{-5}$--$7.83\times10^{-5}$ \\
    $m_{stem2-Nama}$ & Stem 2--Nama migration rate & $5.85\times10^{-5}$ & $4.50\times10^{-5}$--$7.04\times10^{-5}$ \\
    $m_{stem2-MSL}$ & Stem 2--Mende migration rate & $16.2\times10^{-5}$ & $13.8\times10^{-5}$--$18.9\times10^{-5}$ \\
    $m_{stem2-EA}$ & Stem 2--East Africa migration rate & $3.10\times10^{-5}$ & $2.18\times10^{-5}$--$3.65\times10^{-5}$ \\
    \bottomrule
\end{tabular}
\end{table}

\begin{table}[ht]
\caption{
    \label{tab:supp-merger-without-stem-migration}
    \textbf{Best-fit parameters from the Merger-Without-Stem-Migration model.}
    Inferred values are scaled to physical units assuming a generation time of
    29 years. This model gave a log-likelihood of -107,694.
}
\centering
\begin{tabular}[t]{rP{8cm}cc}
    \toprule
    Parameter & Description & Value & 95\% CIs\\
    \midrule
    $N_e$ & Ancestral effective population size & 10990 & 10100--11290 \\
    $N_{stem1}$ & Size of stem 1 lineage between stem 1--stem 2 split and stem 1E--stem 1S split & 278 & 113--606 \\
    $N_{stem2}$ & Size of stem 2 lineage & 27850 & 26500--35060 \\
    $N_{Nama_0}$ & Initial Nama and stem 1S size & 12640 & 11310--12910 \\
    $N_{Nama_F}$ & Final Nama size & 227 & 223--238 \\
    $N_{MSL_0}$ & Initial Mende size & 1190 & 10280--11630 \\
    $N_{MSL_F}$ & Final Mende size & 27440 & 25720--30180 \\
    $N_{EA}$ & Size of East African and stem 1E branch & 9016 & 8680--9140 \\
    $N_{Gumuz_F}$ & Final Gumuz size & 3440 & 3270--3470 \\
    $N_{EP}$ & East African agriculturist size & 13680 & 13120--13690 \\
    $N_{GBR_0}$ & Initial British size & 922 & 920--963 \\
    $N_{GBR_F}$ & Final British size & 12020 & 11790--12430 \\
    $N_{Neand}$ & Neanderthal size & 2100 & 1770--2110 \\
    $T_{stems}$ & Stem split time (years) & 400300 & 381400--410700 \\
    $T_{stem1}$ & Stem 1 split time into stem 1E and stem 1S (years) & 281600 & 154300--320400 \\
    $m_{Nama-MSL}$ & Nama--Mende symmetric migration rate & $0.229\times10^{-5}$ & $0.205\times10^{-5}$--$0.697\times10^{-5}$ \\
    $m_{Nama-EA}$ & Nama--East Africa symmetric migration rate & $4.15\times10^{-5}$ & $3.90\times10^{-5}$--$4.42\times10^{-5}$ \\
    $m_{MSL-EA}$ & Mende--East Africa migration rate & $19.9\times10^{-5}$ & $19.8\times10^{-5}$--$20.8\times10^{-5}$ \\
    $m_{EA-GBR}$ & East Africa--Europe migration rate & $3.99\times10^{-5}$ & $3.34\times10^{-5}$--$3.95\times10^{-5}$ \\
    $m_{EA-EA}$ & Intra-East Africa migration rate & $35.5\times10^{-5}$ & $35.2\times10^{-5}$--$39.6\times10^{-5}$ \\
    $f_{GBR \rightarrow EP}$ & Ancestry proportion of East African agriculturalists from GBR 12ka ($1-f$ from Gumuz) & 0.641 & 0.641--0.661 \\
    $f_{EP \rightarrow Nama}$ & Ancestry proportion from EA pastoralists to Nama 2ka & 0.257 & 0.245--0.264 \\
    $f_{GBR \rightarrow Nama}$ & Ancestry proportion from Europeans to Nama 10 generations ago & 0.156 & 0.152--0.161 \\
    $m_{stems}$ & Stem 1--stem 2 migration rate & $0$ & fixed \\
    $T_{Nama}$ & Time of Nama merger event & 112300 & 101400--116800 \\
    $f_{stem 2 \rightarrow Nama}$ & Proportion of stem 2 ancestry making up initial Nama lineage ($1-f$ from stem 1S) & 0.731 & 0.706--0.769 \\
    $T_{EA}$ & Time of East Africa merger event & 95000 & 94500--101400 \\
    $f_{stem 2 \rightarrow EA}$ & Proportion of stem 2 ancestry making up initial East Africa lineage ($1-f$ from stem 1E) & 0.522 & 0.510--0.564 \\
    $T_{MSL}$ & Time of secondary admixture from stem 2 to Mende & 23510 & 22920--25510 \\
    $f_{stem 2 \rightarrow MSL}$ & Proportion of ancestry from secondary stem 2 admixture to Mende & 0.183 & 0.174--0.196 \\
    \bottomrule
\end{tabular}
\end{table}

\begin{table}[ht]
\caption{
    \label{tab:supp-merger-with-stem-migration}
    \textbf{Best-fit parameters from the Merger-With-Stem-Migration model.}
    Inferred values are scaled to physical units assuming a generation time of
    29 years. This model gave a log-likelihood of -101,618.
    \aprcomment{if the slightly shift, also fix elsewhere in supp and main text}
}
\centering
\begin{tabular}[t]{rP{8cm}cc}
    \toprule
    Parameter & Description & Value & Std. err.\\
    \midrule
    $N_e$ & Ancestral effective population size & 9640 & 6410--11910 \\
    $N_{stem1}$ & Size of stem 1 lineage between Neanderthal split and stem 1E--stem 1S split & 100 & 100--851 \\
    $N_{stem2}$ & Size of stem 2 lineage & 24210 & 22130--26340 \\
    $N_{Nama_0}$ & Initial Nama size & 13440 & 11500--13560 \\
    $N_{Nama_F}$ & Final Nama size & 219 & 214--231 \\
    $N_{MSL_0}$ & Initial Mende size & 11380 & 9690--11290 \\
    $N_{MSL_F}$ & Final Mende size & 27760 & 26820--32280 \\
    $N_{EA}$ & Size of East African Branch & 9100 & 7970--8860 \\
    $N_{Gumuz_F}$ & Final Gumuz size & 3410 & 3270--3570 \\
    $N_{EP}$ & East African agriculturist size & 13510 & 12780--13500 \\
    $N_{GBR_0}$ & Initial British size & 958 & 928--1002 \\
    $N_{GBR_F}$ & Final British size & 12300 & 11850--12600 \\
    $N_{Neand}$ & Neanderthal size & 2520 & 2100--2730 \\
    $T_{stems}$ & Stem split time (years) & 1692000 & 695000--1785000 \\
    $T_{stem1}$ & Stem 1S--stem 1E split time (years) & 478900 & 275600--478300 \\
    $m_{Nama-MSL}$ & Nama--Mende symmetric migration rate & $0.98\times10^{-5}$ & $0.66\times10^{-5}$--$1.57\times10^{-5}$ \\
    $m_{Nama-EA}$ & Nama--East Africa symmetric migration rate & $4.48\times10^{-5}$ & $4.45\times10^{-5}$--$5.52\times10^{-5}$ \\
    $m_{MSL-EA}$ & Mende--East Africa migration rate & $19.7\times10^{-5}$ & $20.0\times10^{-5}$--$21.7\times10^{-5}$ \\
    $m_{EA-GBR}$ & East Africa--Europe migration rate & $3.82\times10^{-5}$ & $3.25\times10^{-5}$--$4.27\times10^{-5}$ \\
    $m_{EA-EA}$ & Intra-East Africa migration rate & $35.9\times10^{-5}$ & $33.7\times10^{-5}$--$40.9\times10^{-5}$ \\
    $f_{GBR \rightarrow EP}$ & Ancestry proportion of East African agriculturalists from GBR 12ka ($1-f$ from Gumuz) & 0.640 & 0.636--0.667 \\
    $f_{EP \rightarrow Nama}$ & Ancestry proportion from EA pastoralists to Nama 2ka & 0.259 & 0.237--0.267 \\
    $f_{GBR \rightarrow Nama}$ & Ancestry proportion from Europeans to Nama 10 generations ago & 0.158 & 0.154--0.167 \\
    $m_{stems}$ & Stem 1--stem 2 migration rate & $12.6\times10^{-5}$ & $3.95\times10^{-5}$--$12.3\times10^{-5}$ \\
    $T_{Nama}$ & Time of Nama merger event & 119500 & 101300--124600 \\
    $f_{stem 2 \rightarrow Nama}$ & Proportion of stem 2 ancestry making up initial Nama lineage ($1-f$ from stem 1S) & 0.698 & 0.694--0.758 \\
    $T_{EA}$ & Time of East Africa merger event & 96300 & 95400--111000 \\
    $f_{stem 2 \rightarrow EA}$ & Proportion of stem 2 ancestry making up initial East Africa lineage ($1-f$ from stem 1E) & 0.515 & 0.514--0.589 \\
    $T_{MSL}$ & Time of secondary admixture from stem 2 to Mende & 25120 & 22210--26300 \\
    $f_{stem 2 \rightarrow MSL}$ & Proportion of ancestry from secondary stem 2 admixture to Mende & 0.187 & 0.182--0.211 \\
    \bottomrule
\end{tabular}
\end{table}
